\mytitle

### 2021-12-08 paper.tex
refine title
adding citation

\newcommand{\mytitle}{The performance gain of instruction-level parallelism on the evaluation of special functions}
\newcommand{\myauthor}{Alexander Voigt}
\newcommand{\Li}{\operatorname{Li}_2}

@@

The dilogarithm \cite{lewin} is a special function, which appears in
many physics applications, for example in the calculation of quantum
corrections in quantum field theory.  The investigation of new models
beyond the Standard Model of particle physics with a large parameter
space require the evaluation of the dilogarithm (and other functions)
billions of times.  Such investigations thus require a fast evaluation
of the dilogarithm.  In the past many time-efficient algorithms have
been proposed \cite{}, which are implemented in program libraries for
numerical physics and mathematics \cite{root,gsl}.

>>>>

\newcommand{\mytitle}{An algorithm for the calculation of the real dilogarithm with instruction-level parallelism}
\newcommand{\myauthor}{Alexander Voigt}
\newcommand{\Li}{\operatorname{Li}_2}

@@

The dilogarithm \cite{lewin} is a special function, which appears in
many physics applications, for example in the calculation of quantum
corrections in quantum field theory.  The investigation of new models
beyond the Standard Model of particle physics with a large parameter
space require the evaluation of the dilogarithm (and other functions)
billions of times.  Such investigations thus require a fast evaluation
of the dilogarithm.  In the past many time-efficient algorithms have
been proposed \cite{}, which are implemented, for example, in program
libraries for numerical physics and mathematics
\cite{root,gsl,cephes}.
